---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BayesSearch

<!-- badges: start -->
<!-- badges: end -->

The package gives functions to implement Bayesian Search theory in R from start to finish. There are helper functions to create valid probability density functions and 3 different search types as well as a custom melt function to aid visualization and analysis.

## Installation

You can install the development version of BayesSearch from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joshyjoshj/BayesSearch")
```

## Creating a valid prior

This is a basic example which shows you how to solve a common problem:

```{r prior}
library(BayesSearch)
## basic example code
```

## Searching a grid sqaure



```{r single_search}

```

## Searching a sequence of squares



```{r search_sequence}

```

## Optimal search sequence



```{r optimal_search}

```

## Extracting data



```{r melt}

```

## Visualisation



```{r plots}

```
